Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2016-01-15 ms.tex
Add date published
Change to PRD style
Increment DCC version

\documentclass[amsmath,amssymb,aps,prx,reprint,nopreprintnumbers,nofootinbib,showpacs]{revtex4-1}
\usepackage[nolist]{acronym}
\usepackage{multirow}
\usepackage{bigdelim}
\usepackage{multirow}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{mathrsfs}
\usepackage{aas_macros}
\usepackage[colorlinks]{hyperref}
\usepackage{protosem}

@@

\title[Rapid-response Bayesian sky localization]{Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients}
\author{Leo P. Singer}
\email{leo.singer@ligo.org}
\author{Larry R. Price}
\email{larryp@caltech.edu}
\affiliation{\acs{LIGO} Laboratory, California Institute of Technology, Pasadena, California 91125, USA}
\received{28 September 2015}
\pacs{04.80.Nn, 04.30.Tv, 02.50.Tt}

@@

\begin{acknowledgements}
This paper has LIGO Document Number LIGO\nobreakdashes-P1500009\nobreakdashes-v7.

>>>>

\documentclass[amsmath,amssymb,aps,prd,reprint,nopreprintnumbers,nofootinbib,showpacs]{revtex4-1}
\usepackage[nolist]{acronym}
\usepackage{multirow}
\usepackage{bigdelim}
\usepackage{multirow}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{mathrsfs}
\usepackage{aas_macros}
\usepackage[colorlinks]{hyperref}
\usepackage{protosem}

@@

\title[Rapid-response Bayesian sky localization]{Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients}
\author{Leo P. Singer}
\email{leo.singer@ligo.org}
\author{Larry R. Price}
\email{larryp@caltech.edu}
\affiliation{\acs{LIGO} Laboratory, California Institute of Technology, Pasadena, California 91125, USA}
\received{28 September 2015}
\published{14 January 2016}
\pacs{04.80.Nn, 04.30.Tv, 02.50.Tt}

@@

\begin{acknowledgements}
This paper has LIGO Document Number LIGO\nobreakdashes-P1500009\nobreakdashes-v8.
